---
title: "HW 03 - Great Lakes Fish Datasets"
author: "Insert your name here"
date: "Insert date here"
output: html_document
---

## Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
```

```{r load-data, message = FALSE}
catch_data <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-06-08/fishing.csv')

fish_stock <- read_csv("data/great-lakes-fish-stock.csv")
```

## Exercises

### Exercise 1

Remove this text, and add your answer for Exercise 1 here.

### Exercise 2

Remove this text, and add your answer for Exercise 2 here.

### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

### Code chunks provided

Remember to change eval = FALSE, to eval = TRUE, when you are ready to run the code/knit the document.

```{r finalize-fish-stock, eval = FALSE}
fish_stock_yearly <- fish_stock_yearly %>% 
  rename(year = YEAR) %>% 
  mutate(stock_weight_yr_lbs = as.integer(STOCK_WEIGHT_YR * 0.454 / 1000)) %>% # 1 lb = 1 kg * 0.454
  select(year, stock_weight_yr_lbs)
```

```{r finalize-catch-data, eval = FALSE}
catch_data <- catch_data %>% 
  rename(catch_weight_yr_lbs = values)
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.
